Title Goes Here

### 2024-05-31 analysis/paper/paper.qmd
QS

@@

@@

>>>>

fig_ave_length_EEO_per_year <- 
ggplot(jobdata_EEO_year_tally) +
  aes(year_ad_posted) +
  geom_bar() +
  scale_x_discrete(name = "") +
  ylab("Average length of EEO statement by year") +
  theme_minimal(base_size = 28) +
  guides(x = "none")

@@

EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE) %>%
  drop_na()

@@

```{r}
ggplot(EEO_word %>% 
         filter(n > 20), 
       aes(x = reorder(word, n), 
           y = n)) +
  geom_col() +
  labs(x = "Words", 
       y = "Frequency", 
       title = "Word Frequency") +
  coord_flip()
```

```{r}
# explore QS rankings

qs_rankings <- 
  readxl::read_excel("analysis/data/raw_data/2024 QS WUR by Subject - Public Results (for qs.com)_48.xlsx", sheet = "Archaeology", skip = 12)

jobdata %>% 
  mutate(Institution = str_remove(name_of_hiring_university,
                                  " \\(.*\\)")) %>% 
  mutate(Institution = case_when(
    # modify the school name to match with the name in the QS list
    Institution == "Ohio State University-Main Campus" ~ "The Ohio State University",
  "Cambridge" ~ "University of Cambridge",
  "Cambridge University" ~ "University of Cambridge",
  "Keble College" ~ "University of Oxford",
  "University of California-Berkeley" ~ "University of California, Berkeley (UCB)",
"University of California-Los Angeles" ~ "University of California, Los Angeles (UCLA)",
"University of Tuebingen" ~ "Eberhard Karls Universität Tübingen",
"Universität Tübingen" ~ "Eberhard Karls Universität Tübingen",
"Arizona State University Campus Immersion" ~ "Arizona State University",
"Kiel University" ~ "Christian-Albrechts-University zu Kiel",
"University of Arizona" ~ "The University of Arizona",
"The Pennsylvania State University" ~ "Pennsylvania State University",
"University of Bologna" ~ "Alma Mater Studiorum - University of Bologna",
"University of Sydney" ~ "The University of Sydney",
"University of Copenhagen, Saxo Institute" ~ "University of Copenhagen",
"The University of Texas at Austin" ~ "University of Texas at Austin",

    .default = as.character(Institution)
  )) %>% 
  select(Institution) %>% 
  left_join(qs_rankings) %>% 
  drop_na(`2024`) %>% 
  distinct(Institution, .keep_all = TRUE) %>% 
  View()
